Galois Characterization of Function Fields of \\ Transcendence Degree $1$ over Number Fields

### 2016-11-26 Master Thesis/synopsis.tex
Add remark after 4.2

>>>>

\begin{remark}
Consider $\overline{K}'' = \overline{K}'\otimes_{\overline{k'}}\overline{k}$ via the isomorphism $\varphi: \overline{k'}\to \overline{k}$. If we replace $\sigma: G_K\to G_{K'}$ with the composition
\[ \begin{tikzcd}
G_K \ar[r, "\sigma"] & G_{K'} \ar[r] & G_{K'}
\end{tikzcd} \]
where the second map is induced by the isomorphism $\overline{K''}\to\overline{K'},\ x\otimes y\mapsto \varphi^{-1}(y)\cdot x$, we may assume that $k=k'$, $\overline{k} = \overline{k'}$ and $\varphi:\overline{k}\to\overline{k}$, $\sigma: G_k\to G_k$ are identities.
\end{remark}
